---
title: 'Final Project'
author: "Marcus Ortiz"
date: "05/19/2022"
output:
  pdf_document:
    includes:
      in_header: header.tex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
library(tidyverse)
library(dplyr)
library(lm.beta)
data1<-read.csv("Life Expectancy Data.3.csv")
data2<-na.omit(data1)
head(data2)
data2<-data2 %>% 
  mutate(status2=case_when(
    Status=="Developing"~0,
    Status=="Developed"~1
  ))
```


```{r}
mod1<-lm(Life.expectancy.Y.~Adult.Mortality+infant.deaths+Alcohol+percentage.expenditure+BMI+under.five.deaths+Total.expenditure+Diphtheria+HIV.AIDS+Income.composition.of.resources+Schooling+status2+Hepatitis.B+Measles+GDP+Population+thinness..1.19.years+thinness.5.9.years+Polio,data=data2)
summary(mod1)

```





```{r}
mod2<-lm(Life.expectancy.Y.~Adult.Mortality+infant.deaths+Alcohol+percentage.expenditure+BMI+under.five.deaths+Total.expenditure+Diphtheria+HIV.AIDS+Income.composition.of.resources+Schooling+status2,data=data2)
summary(mod2)

```

#Ho:beta13=beta14=beta15=beta16=beta17=beta18=beta19=0

#Ha:The null is not true(one of the betas!=0)

```{r}
anova(mod2,mod1)
qf(0.80,7,1629)
qf(0.9,7,1629)
qf(0.95,7,1629)
qf(0.975,7,1629)
qf(0.99,7,1629)
qf(0.999,7,1629)

```

#Because the F-stat for the anova test between model 1 and model 2 is 1.3222, we fail to reject the null hypothesis for significance level 80% and onward.Therefore we conclude that predictors Hepatitis B, Measles,GDP, Population, thinness 1-19 years, thinness 5-9 years and Polio are statistically insignificant and can be removed from the model.




```{r}
mod3<-lm(Life.expectancy.Y.~Adult.Mortality+infant.deaths+percentage.expenditure+BMI+under.five.deaths+Diphtheria+HIV.AIDS+Income.composition.of.resources+Schooling,data=data2)
```

#Ho:beta3=beta7=beta12=0

#Ha:The null is not true(beta3, beta7, or beta1!=0)


```{r}
anova(mod3,mod2)
qf(0.95,3,1636)
qf(0.975,3,1636)
qf(0.99,3,1636)
qf(0.999,3,1636)

```

#The F-stat for this anova test between model 2 and model 3 is 5.45. Therefore,we fail to reject the null at significance level 99.9%. We can conclude that predictors alcohol, total expenditure, and status are statistically insignificant and thus can be removed from the model.



```{r}
summary(mod3)
confint(mod3)

```
#beta1<-The head count for adults that have died


#beta2<-The head count for infants that have died

#beta3<-The percentage of total expenditure 

#beta4<-The average BMI per person

#beta5<-The head count for kids that have died under the age of 5

#beta6<-The head count for people that have Diphtheria

#beta7<-The percentage of the population that has HIV or AIDS

#beta8<-The relative share of income source expressed as a percentage of total income

#beta9<-The average amount of years of schooling per person